### 2019-12-15 article.tex
horizontal architecture and some descriptions added

\usepackage{textcomp}
%\usepackage{mathpazo}

@@

Furthermore, our model's accuracy can be obtained in two different aspects. The first one would be the correctness of each time-slice prediction ($\bar{C}_{i,t}$), while the second, is the accuracy of disease diagnosis ($\bar{C}_i$), and we are mostly interested in the later.

\begin{figure}
	\includegraphics[width=\linewidth]{images/cnnArch}
	\caption{proposed Bayesian 3D CNN architecture}
	\label{fig:cnnArch}
\end{figure}

@@

>>>>

\usepackage{textcomp}
\usepackage{graphicx}
\usepackage{caption}
%\usepackage{mathpazo}

@@

@@

Furthermore, our model's accuracy can be obtained in two different aspects. The first one would be the correctness of each time-slice prediction ($\overline{C}_{i,t}$), while the second, is the accuracy of disease diagnosis ($\overline{C}_i$), and we are mostly interested in the later. Both of the mentioned statistics can be calculated using Equation \eqref{eq:meanCorrectness}.

\begin{figure*}
	\includegraphics[width=\linewidth]{images/cnnArchHorizontal}
	\caption{Proposed architecture}
	\label{fig:cnnHorizontalArch}
\end{figure*}

\begin{eqnarray}
\label{eq:meanCorrectness}
\overline{C_{i,t}} &=& {{\sum_{i=1}^{m} \sum_{t=1}^{T (=198)} C_{i,t} } \over {m \times T} } \\ 
\overline{C_i} &=& {{\sum_{i=1}^{m} C_i } \over {m } }  \nonumber 
\end{eqnarray}

As can be seen in Figure \ref{fig:cnnHorizontalArch}, we have added different dropout units between our convolution and pooling layers to avoid overfitting, decrease variance and make convergence to appropriate weights faster. In addition to that, dropout probabilities increase in each layer because layers with less free parameters have a greater chance to train well even if they are less frequently updated. In other words, a huge number of parameters cannot tune acceptably with a small amount of data while getting omitted a lot. On the other hand, as there are only 16 weights in the first fully connected layer, higher dropout probabilities can speed up the training process.

\begin{figure}
	\includegraphics[width=\linewidth]{images/cnnArch}
	\caption{Proposed Bayesian 3D CNN architecture}
	\label{fig:cnnArch}
\end{figure}
